%\todo{freewriting:} 
%what did i want to do? 
The goal of this work was to find a sol-gel doctor blading process resulting in a insulating zirconium ceramic on top of steel.
This structure then can be used as substrate for thin layer photo voltaics. 
The ceramic needs to be homoegeneous and defect free in order to insulate properly.
%what was done? 
A suitable recipe was found\cite{Hu2016} and the process variables were optimized via \gls{emma}. 
The recipe was improved by increasing its stability. 
The best parameters found by the emma optimization were 
$c_{zr}=2$, $\lambda=10$, $v_{DB}=10$, $T_{DB}=40$, $v_{cal}=120$ and $T_{cal}=300$.
%\todo{$T_{cal}=300$}. 
%welche methoden wurden dafür verwendet? 
After optimzation the data was analysed with further machine learning methods like kernel ridge regression, support vector regression and linear regression. 
The comparisson of methods showed that \gls{emma} performed well on predicting the correlation between conductance and process variables. 
%was wurde herausgefunden? 
A strong correlation of calcination temperature and conductance in the bereich of 300--400\oc{}. 
%was kann noch herausgefundne werden und wie? 
Next steps include to investigate if the correlation of condactance and calcination temperature are statistically significant or due to small sample size. 
The aging process could be examined via infra red spectroscopy. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\iffalse
was kann noch veraendert werden? 
humidity 
solution age
vdb and tdb on g and phd 
Tcal on g and phd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5

Making of the solution for the sol-gel process:
For a single concentrated solution \ml{0.05} of \gls{zrpro} are added while stirring to \ml{4.95} of \gls{buoh} and stirred for \minutes{15}. 
\ml{0.013} (or one molar equvilent of Zr) of \gls{acac} is added to the stirring solution. 
After another \minutes{15} \ml{1} of acetic acid is added and stirred for \minutes{30} to stabilize the solution up to \h{24}. 

The concentration can be increased up to 5 times being stable for a minimum of \h{4}. 
The sol-gel process produces am homogeneous transparent crystalline zirconia oxide layer. 
homogeneity can be mainly controlled via blade velocity and temperature and layers can be stacked.

It should have been also verglichen with grid search with comparable size
but most time was used to find a vernuenfig base recipe and process

It is still very human 
Der process is - as it the case with all ML and most fitting processes - is very abhaengig von hyper parameters, 
In the current work population size, number of generations, and most importantly boundaries (grenzen). 
\fi
